### 2020-02-14 latex_user_manual/appendix/GPL3_SPAMDA_license.tex
Building the version of the paper for the journal "Advances in Engineering Software"

Copyright (c) 2017-2018 by AYRNA Research Group. https://www.uco.es/ayrna/
	\begin{quote}
	Authors: 
		\begin{quote}
			Antonio Manuel Gómez Orellana, Juan Carlos Fernández Caballero,
			Manuel Dorado Moreno, Pedro Antonio Gutiérrez Peña and 
			César Hervás Martínez.
		\end{quote}
	\end{quote}

@@

Contact information:

Juan Carlos Fernández Caballero, PhD.

@@

Address: University of Cordoba, Department of Computer Science
and Numerical Analysis, AYRNA Research Group, Rabanales Campus,
Einstein Building, 3rd floor. Road Madrid-Cadiz, Km 396-A.
14071 - Cordoba (Spain).

>>>>

Copyright (c) 2017-2020 by AYRNA Research Group. https://www.uco.es/ayrna/
	\begin{quote}
	Authors: 
		\begin{quote}
			Antonio Manuel Gómez Orellana, Juan Carlos Fernández Caballero,
			Manuel Dorado Moreno, Pedro Antonio Gutiérrez Peña and 
			César Hervás Martínez.
		\end{quote}
	\end{quote}

@@

\vspace{0.50cm}
Contact information:

% \begin{quote}
Antonio Manuel Gomez Orellana.

email: am.gomez@uco.es

Address: University of Córdoba, Department of Computer Science and Numerical Analysis, Rabanales Campus, AYRNA Research Group, Einstein Building, 3rd floor. Road Madrid-Cádiz, Km 396-A. 14071 - Córdoba (Spain)
% \end{quote}

\vspace{0.50cm}

% \begin{quote}
Juan Carlos Fernández Caballero.

@@

Address: University of Córdoba, Department of Computer Science and Numerical Analysis, Rabanales Campus, AYRNA Research Group, Einstein Building, 3rd floor. Road Madrid-Cádiz, Km 396-A. 14071 - Córdoba (Spain)
% \end{quote}
